---
title: "neato"
author: "Nicholas Tierney"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = F}

library(dplyr)
library(knitr)
library(rpart)

```


# Introduction

This is the draft vignette for the package neato.

It's probably going to have a bunch of different sections, like `plotting`, and `tables` and that sort of thing.

# Using `importance_table`

So here's the go for importance table, you want to get the variable importance information, and here's how you can do it.

First, let's take an rpart fitted object
```{r}

fit.rpart <- rpart(Kyphosis ~ Age + Number + Start, data = kyphosis)

```

And let's turn it into an importance table

```{r}

# importance_table(fit.rpart)

```

You can even use the pipe operator `%>%`

```{r}

# fit.rpart %>% importance_table

```

And then if you want you can make a table using the `kable` function from `knitr`

```{r}

# fit.rpart %>% importance_table %>% kable

```


